\documentclass[a4paper]{article}
    \usepackage[margin=0.98in]{geometry}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Gurpreet Singh}}\\
	London, Ontario $\cdot$ gsingh95@uwo.ca $\cdot$ 519-317-0782 $\cdot$ gurpreetsingh.me\\
\end{center}

\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{University Of Western Ontario}\hfill London, Ontario\\
Honors Specialization in Computer Science with a Minor in Software Engineering \hfill Grad: May 2018\\
\vspace{2mm}

\vspace*{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Ark Blockchain} \hfill Remote\\
\textit{Software Developer (Community)} \hfill June 2017 | Feb 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Develop software and community libraries for the Ark Blockchain open-source organization.
	\item Created and maintain ark-java and ark-kotlin repositories which allow an easy interface to the blockchain from either language.
    \item Developed Cordova plugin for the Ledger hardware wallet allowing JS applications to interface with native Android and iOS hardware for Ledger authentication.
    \item Created an architecture to connect IoT devices to the blockchain using on-chain data storage with a custom designed protocol.\\
    \item 4-time winner of the monthly development bounty award.
\end{itemize}

\textbf{IBM Canada} \hfill Markham, Ontario \& Remote\\
\textit{Infosphere MDM Software Engineer} \hfill May 2016 | Aug 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and implemented frameworks to assist with end to end regression tests, allowing for continuous build deployment, and performance evaluation through each release cycle of MDM.
	\item Lead a team of developers to create a microservice management architecture for the delivery platform and converted existing tools to microservices.
	\item Pitched new technologies to the team. Held one on one sessions with developers and managers to explain how to use Git, Docker, etc.
	\item Worked extensively with DevOps tools like Docker, Travis, Jenkins and Git to develop and deploy tooling.
\end{itemize}

\textbf{Tutor Hero} \hfill London, Ontario\\
\textit{Chief Technology Officer} \hfill Sept 2013 | Nov 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Created a Kijiji-like web app where tutors can market their services and students can meet verified tutors. This brokerage website was developed in Python using the Django framework.  
	\item This role consisted of leading the development of the web-app, recruiting interns, and managing a small development team to meet tight deadlines. 
	\item Tutor Hero grew to 1600 tutors across 17 cities in Canada in six months. www.tutorhero.ca
\end{itemize}

\textbf{United Steelworkers (USW)} \hfill Toronto, Ontario\\
\textit{Information Technology Intern} \hfill May 2015 | Sept 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed websites for political representatives and Java applications to automate responsibilites
	\item Presented weekly analytical reviews of online content.
\end{itemize}

\header{Projects}
{\textbf{Cloud Drive} \sl C, Valgrind, Redis, TCP/UDP} \hfill https://github.com/Guppster/Drive\\
\vspace*{1mm}
Cloud drive networking implementation written in C using Redis. Functions like Dropbox.\\
\vspace*{2mm}
{\textbf{Microservices-Core} \sl Rust, Go, Kotlin, C, Java} \hfill https://github.com/Guppster/MicroservicesStack\\
\vspace*{1mm}
Central microservice management framework that enables microservice deployment, registration, querying and execution.\\
\vspace*{2mm}
{\textbf{HackingCancer} \sl Java, Swing} \hfill https://github.com/Guppster/HackingCancer\\
\vspace*{1mm}
Game design project using the power of crowdsourcing to assist cancer research. Winner of HackWestern\\
\vspace*{2mm}
{\textbf{Faulty} \sl } \hfill https://github.com/Guppster/Faulty\\
\vspace*{1mm}
Fault Localization software that captures faults within large codebases based on analysis of bug reports or issues.\\
\vspace*{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Java 8, C, C\#, JS, Ruby, Lua, Go, Rust, Kotlin, Perl, Assembly \\
	DevOps Tools:          & Git, Jenkins, Travis, Docker, Gradle, Maven, Bluemix \\
\end{tabular}

\end{document}
